A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-01-25 paper/draft.tex
include maps into paper

>>>>

In this section, I provide descriptive statistics that illustrate broader patterns in the distribution of party affiliated bureaucrats at the municipal level in Brazil. Figure \ref{fig:map_pooled} illustrates the subnational distribution of party affiliation in Brazil for the year of 2015. There are a few patterns that emerge.

First, that the distribution of partisan affiliation varies significantly over the national territory, with its predominance in the Northeast, as well as in the Northern regions of the country. The Midwest and Southeast appear to have the lowest prevalence of partisan affiliation. Second, that there is wide variation with respect to the prevalence of partisanship. In particular, some municipalities are almost entirely occupied by party members, with over 60 percent of its workforce affiliated to some party.

\begin{figure}
    \includegraphics{figures/maps/pooled.png}
    \caption{\textbf{Proportion of party-affiliated members by municipality (2015)}. Darker colors indicate a larger degree of partisan affiliation. This visualization includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}
